We are delighted to present the Proceedings of the 15th International Natural Language Generation Conference (INLG 2022). After 2 years being held virtually due to the COVID-19 pandemic, this year the conference was a hybrid event, happening virtually and physically in Waterville, Maine, the United States between July 18-22, 2022.

INLG 2022 was locally organized by the Davis Institute for AI at Colby College thanks to the wonderful work of Amanda Stent, the Local Chair.

The INLG conference is the main international venue for the discussion of the computational task of Natural Language Generation (NLG) and its wide-range of applications, including data-to-text, text-to-text and vision-to-text approaches. 

This year the conference consisted of a varied set of events. It started with a tutorial on "Artificial Text Detection", followed by the "NLG4Health" workshop whose proceedings included 4 accepted papers, a keynote speaker and a panel.

The main conference took place on July 19-21. Excluding Generation Challenges, we received a total of 51 committed submissions from which 19 were accepted as long papers, 6 as short papers and 4 as demo papers.

Generation Challenges, a set of shared tasks, was also presented during the main conference. The event proceedings consisted of 2 new shared-task proposals and the presentation of 3 completed ones. Besides the overview papers, the completed shared-tasks summed a total of 12 system descriptions.

This year INLG had 4 keynote speakers who did important contributions to the field:

Dimitra Gkatzia, Edinburgh Napier University
Emiel Krahmer, Tilburg University
Margaret Mitchell, Huggingface
Mohit Bansal, University of North Carolina (UNC) Chapel Hill

A panel on "Ethics and NLG" was also introduced in INLG 2022. We would like to thank the members, Nina da Hora, Sebastian Gehrmann, Sabelo Mhlambi, Nava Tintarev and Frank Schilder, as well as the moderator, Margaret Mitchell.

Last but not least, INLG 2022 closed with a hackathon on "Automatic Generation of Reports about the Gulf of Maine" on July 22nd.

The event was financially supported by:

ARRIA (Gold)
Google (Gold)
HuggingFace (Silver)
AX Semantics (Bronze)
aiXplain (Bronze)

It is also important to mention that the 15th version of INLG would not be possible without the help of Area Chairs and Reviewers for whom we express our entire gratitude and that we relied on the expertise of Ehud Reiter and Emiel van Miltenburg, SIGGEN representatives.

Samira Shaikh
Thiago Castro Ferreira

INLG 2022 Programme Chairs

Program Chair
Samira Shaikh
Thiago Castro Ferreira

Local Chair
Amanda Stent

Invited Speakers
Dimitra Gkatzia, Edinburgh Napier University
Emiel Krahmer, Tilburg University
Margaret Mitchell, Huggingface
Mohit Bansal, University of North Carolina (UNC) Chapel Hill

SIGGEN Representatives
Ehud Reiter
Emiel van Miltenburg

Tutorial and Hackathon Chair
Joshua Maynez

Publication Chair
MIruna Clinciu

GenChal Chair
Anastasia Shimorina

Sponsor Chair
Dave Howcroft

Social Media Chair
Luou Wen (Lilly)

Area Chairs
Albert Gatt
Chris van der Lee
Claire Gardent
Dimitra Gkatzia
Fei Liu
Malihe Alikhani
Michael White
Saad Mahamood
Tirthankar Ghosal
Yufang Hou

Local Organizing Team
Amy Poulin
Charlotte Buswick
Jake Rogers
